Deciphering the Trends: A Comprehensive Analysis of US Birth Rates and Educational Attainment from 1980 to 2020

### 2024-02-04 outputs/paper/paper.qmd
paper edits

```{r}
library("tidyverse")
data <- read.csv("~/usa_birthrate/inputs/data/fig_1.csv")

@@

```

```{r}
data <- read.csv("~/usa_birthrate/inputs/data/fig_2e.csv")

@@

```

```{r}

data <- read.csv("~/usa_birthrate/inputs/data/fig_5.csv")

@@

```
```{r}

data <- read.csv("~/usa_birthrate/inputs/data/fig_4.csv")
ggplot() + 
    geom_line(data = data, aes(x = year, y = brate_1519, color = "15-19")) +
    geom_line(data = data, aes(x = year, y = brate_2024, color = "20-24")) +
    geom_line(data = data, aes(x = year, y = brate_2529, color = "25-29")) +
    geom_line(data = data, aes(x = year, y = brate_3034, color = "30-34")) +
    geom_line(data = data, aes(x = year, y = brate_3539, color = "35-39")) +
    geom_line(data = data, aes(x = year, y = brate_4044, color = "40-44")) +
    theme_minimal() +
    labs(title = "US Birth Rates by Age Group (1980-2020)",
         x = "Year",
         y = "Birth Rate",
         color = "Age Group")

```

>>>>

```{r}
#| label: fig-1
library("tidyverse")
data <- read.csv("~/usa_birthrate/inputs/data/fig_1.csv")

@@

```
@fig-1
```{r}
#| label: fig-2
data <- read.csv("~/usa_birthrate/inputs/data/fig_2e.csv")

@@

```
@fig-2
```{r}
#| label: fig-3
data <- read.csv("~/usa_birthrate/inputs/data/fig_5.csv")

@@

```
@fig-3
```{r}
#| label: fig-4
data <- read.csv("~/usa_birthrate/inputs/data/fig_4.csv")
ggplot() + 
    geom_line(data = data, aes(x = year, y = brate_1519, color = "15-19")) +
    geom_line(data = data, aes(x = year, y = brate_2024, color = "20-24")) +
    geom_line(data = data, aes(x = year, y = brate_2529, color = "25-29")) +
    geom_line(data = data, aes(x = year, y = brate_3034, color = "30-34")) +
    geom_line(data = data, aes(x = year, y = brate_3539, color = "35-39")) +
    geom_line(data = data, aes(x = year, y = brate_4044, color = "40-44")) +
    theme_minimal() +
    labs(title = "US Birth Rates by Age Group (1980-2020)",
         x = "Year",
         y = "Birth Rate",
         color = "Age Group")

```
@fig-4
